Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-18 ieee_paper.tex
working on code presentation
temp
code almost ready
final figure 8?
captioning in small touch up

\begin{figure*}
  \centering
  %\subfigure[Source code}
  \includegraphics[width=0.8\textwidth]{figures/source_code.pdf}%
  \label{fig:source}
  \caption{Source Code}
\end{figure*}
%\newfig{figures/source_code.pdf}{6in}{Source code}{fig:source}

>>>>

\begin{figure*}
  \centering
  %\subfigure[Source code}
%  \includegraphics[width=0.8\textwidth]{figures/source_code.pdf}%

\subfigure[Source code]{\includegraphics[clip=true,trim=4.5cm 11cm 4cm 4.2cm,width=.6\linewidth]{code.pdf}}%
\subfigure[Content of the vector registers]{\hspace{-0.07\linewidth}\includegraphics[width=.5\linewidth]{figures/code-annote.pdf}}

\caption{Code snippet of the multiplication of 4 vectors with 4
  matrices. When a line changes the content of a vector register its
  content is shown on the right. The effects of swizzling and
  permutations are highlighted using a color code.}
\label{fig:code}

\end{figure*}
%\newfig{figures/source_code.pdf}{6in}{Source code}{fig:source}
